---
title: "test code"
author: "Eddie Kingston"
date: "1/30/2023"
output: pdf_document
---

```{r}
plot_net_tribes <- function(g, m) { # Plot both tribes together during the premerge phase
  g <- graph_from_adjacency_matrix(g) # convert Gurundji matrix to graph
  m <- graph_from_adjacency_matrix(m) # convert Makassan matrix to graph
  for (i in 1:length(V(igraph::union(g,m))$name)) {
   if (V(igraph::union(g,m))$name[i] %in% cast_g1) {
     V(igraph::union(g,m))$color[i] <- "red"
     }
    else { 
      V(igraph::union(g,m))$color[i] <- "green" 
      }
    } #color vertices red if part of Gurundji, green if part of Makassan
  V(igraph::union(g,m))$color <- remove.na(V(igraph::union(g,m))$color)
  plot(igraph::union(g,m),vertex.size=27, edge.arrow.size=0.5, layout = layout(igraph::union(g,m)))
}
plot_net_tribes(ep1_day1_g1,ep1_day1_g1)
```


```{r}
ep1_day1_g1 <- graph_from_adjacency_matrix(ep1_day1_g1)
ep1_day1_m1 <- graph_from_adjacency_matrix(ep1_day1_m1)
```

```{r}
un_mat <- as_adjacency_matrix(ep1_day1_g1 %u% ep1_day1_m1, sparse = F)
```

```{r}
ep1_day1_g1 <- as_adjacency_matrix(ep1_day1_g1, sparse = F)
ep1_day1_m1 <- as_adjacency_matrix(ep1_day1_m1, sparse = F)
un_graph <- graph_from_adjacency_matrix(un_mat) 
```


```{r}
vertex_attr(ep1_day1_g1)
```

```{r}
ep1_day1.5 <- union(ep1_day1_g1,ep1_day1_m1)
V(ep1_day1.5)$color <- rep(0,length(V(ep1_day1.5)$name))
for (i in 1:length(V(ep1_day1.5)$color)) {
  ifelse(V(ep1_day1.5)$name[i] %in% cast_g1, V(ep1_day1.5)$color[i] <- "red", V(ep1_day1.5)$color[i] <- "green")
}
plot(ep1_day1.5)
```

```{r}
g <- matrix(0,nrow=4,ncol=4,dimnames=list(c("a","b","c","d"),c("a","b","c","d")))
g
```

```{r}
# g <- as_adjacency_matrix(g)
g[1,2] <- 1
g[2,c(1,3)] <- 1
g[3,c(1,2)] <- 1
```

```{r}
g <- graph_from_adjacency_matrix(g)
plot(g,vertex.size=27, edge.arrow.size=0.5, layout = layout(g))
```
```{r}
cast <- c("a","b","c","d")
ally1 <- c("a|b", "b|a")
ally2 <- c("b|c","c|b")
ally <- as.matrix(c(ally1,ally2))
plot(g)
```

```{r}
# Sort through the cast and sort through alliance. For each other column, if there is an edge between them AND
# they're both in an alliance together, color the edge green. Otherwise color it orange.
E(g)$color <- "grey50"
for (i in 1:length(E(g))) {
  ifelse(attr(E(g),"vnames")[i] %in% ally, E(g)$color[i] <- "green", E(g)$color[i] <- rgb(1,0,0,0.3))
}
plot(g)
```

```{r}
row_order <- sort(rownames(un_mat))
col_order <- sort(colnames(un_mat))
un_mat <- un_mat[row_order,col_order]
un_graph <- graph_from_adjacency_matrix(un_mat)
plot(un_graph)
```
```{r}
ep1_day1 <- ep1_day0
ep1_day1 <- ep1_day1[-2,-2] # Coco
ep1_day1 <- ep1_day1[-6,-6] # Josh
ep1_day1 <- ep1_day1[-9,-9] # Megan
ep1_day1 <- ep1_day1[-5,-5] # Jacob
ep1_day1 <- ep1_day1[-6,-6] # Liz
ep1_day1 <- ep1_day1[-11,-11] # Zanny
ep1_day1 <- ep1_day1[-3,-3] # Denver
ep1_day1 <- ep1_day1[-3,-3] # Dio
```

Alliance list:
1: Denver, Megan O, Mel (Made Ep 1 Day 3, dissolved at start of Ep 8)
2: Denver, Megan O, Mel, Zanny (Made Ep 2 Day 7, became (1) at s)
3: Denver, Megan O, Mel, Neb, Zach (Made Ep 2 Day 7 at )
4: Clown, Denver, Dio
5: Clown, Dio, Liz
6: CT, Lisa, Mel, Zach
7: Clown, Dio, Liz, Mark
8: Denver, Dio, Neb
--MERGE--
9: Denver, Dio, Megan O
10: CT, Lisa, Zach
11: Clown, Denver, Dio, Megan O
12: Clown, Mark, Neb
13: CT, Mark, Neb
14: Clown, CT, Mark, Neb
15: Clown, CT, Mark, Megan O
16: Clown, CT, Neb
17: CT, Megan O, Neb

1 c 2
1 c 3
5 c 7
10 c 6
4 c 11
12 c 14
13 c 14
16 c 14
12 U 13 U 16 = 14

Clown -> CT, Denver, Dio, Liz, Mark, Megan O, Neb 
CT -> Clown, Lisa, Mark, Megan O, Mel, Neb, Zach 
Denver -> Clown, Dio, Megan O, Mel, Neb, Zach, Zanny
Dio -> Denver, Liz, Mark, Megan O, Neb 
Lisa -> CT, Mel, Zach 
Liz -> Clown, Dio, Mark
Mark -> Clown, Dio, Liz, Megan O, Neb
Megan O -> Clown, CT, Denver, Dio, Mark, Mel, Neb, Zach, Zanny
Mel -> CT, Denver, Lisa, Megan O, Neb, Zach, Zanny
Neb -> Clown, CT, Denver, Dio, Mark, Megan O, Mel, Zach
Zach -> CT, Denver, Lisa, Megan O, Mel, Neb
Zanny -> Denver, Megan O, Mel
```{r}
ep6_day14_m2 <- as_adjacency_matrix(delete_vertices(graph_from_adjacency_matrix(ep6_day14_m2),"Zanny"))
ep7_day16 <- as_adjacency_matrix(graph_from_adjacency_matrix(ep6_day14_g2) %u% graph_from_adjacency_matrix(ep6_day14_m2))
ep7_day16 <- ep7_day16[sort(rownames(ep7_day16)),sort(colnames(ep7_day16))]
```


```{r}
density <- matrix(NA,16,16,dimnames=list(cast,eps))
dens <- function(c,epstats) {
  for (i in cast) {
  if (i %in% rownames(epstats)) {
    density[i,c] <- epstats[i,2]
  }
  }
}
dens(1,ep1_day3_stats)
```

```{r}
density <- matrix(NA,16,16,dimnames=list(cast,eps))
for (i in cast) {
if (i %in% rownames(ep1_day3_stats)) {
  density[i,1] <- ep1_day3_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep2_day7_stats)) {
  density[i,2] <- ep2_day7_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep3_day10_stats)) {
  density[i,3] <- ep3_day10_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep4_day10_stats)) {
  density[i,4] <- ep4_day10_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep5_day13_stats)) {
  density[i,5] <- ep5_day13_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep6_day14_stats)) {
  density[i,6] <- ep6_day14_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep7_day16_stats)) {
  density[i,7] <- ep7_day16_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep8_day19_stats)) {
  density[i,8] <- ep4_day10_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep9_day22_stats)) {
  density[i,9] <- ep9_day22_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep9_day23_stats)) {
  density[i,10] <- ep9_day23_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep9_day24_stats)) {
  density[i,11] <- ep4_day10_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(ep10_day26_stats)) {
  density[i,12] <- ep10_day26_stats[i,2]
}
}
for (i in cast) {
if (i %in% rownames(finale_day27_stats)) {
  density[i,13] <- finale_day27_stats[i,2]
}
}
density
```

```{r}
vert_dens_df <- data.frame(
  cast = sort(rep(cast,16)),
  eps = rep(eps,16)
)
vert_dens_df <- vert_dens_df %>% mutate(
  densities = c(density["Clown",],density["Coco",],density["CT",],density["Denver",],density["Dio",],density["Jacob",],density["Josh",],density["Lisa",],density["Liz",],density["Mark",],density["Megan",],density["Megan O",],density["Mel",],density["Neb",],density["Zach",],density["Zanny",])
)
ggplot(vert_dens_df, aes(x=eps,y=densities, group = cast)) + geom_line(aes(color = cast)) + ggtitle("Vertex Densities of Cast Per Episode") + xlab("Episodes") + ylab("Densities") + theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
```

```{r}
between <- matrix(NA,16,16,dimnames=list(cast,eps))
for (i in cast) {
if (i %in% rownames(ep1_day3_stats)) {
  between[i,1] <- ep1_day3_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep2_day7_stats)) {
  between[i,2] <- ep2_day7_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep3_day10_stats)) {
  between[i,3] <- ep3_day10_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep4_day10_stats)) {
  between[i,4] <- ep4_day10_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep5_day13_stats)) {
  between[i,5] <- ep5_day13_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep6_day14_stats)) {
  between[i,6] <- ep6_day14_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep7_day16_stats)) {
  between[i,7] <- ep7_day16_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep8_day19_stats)) {
  between[i,8] <- ep4_day10_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep9_day22_stats)) {
  between[i,9] <- ep9_day22_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep9_day23_stats)) {
  between[i,10] <- ep9_day23_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep9_day24_stats)) {
  between[i,11] <- ep4_day10_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(ep10_day26_stats)) {
  between[i,12] <- ep10_day26_stats[i,3]
}
}
for (i in cast) {
if (i %in% rownames(finale_day27_stats)) {
  between[i,13] <- finale_day27_stats[i,3]
}
}
between
```

```{r}
betweenness_df <- data.frame(
  cast = sort(rep(cast,16)),
  eps = rep(eps,16)
)
betweenness_df <- betweenness_df %>% mutate(
  betweenness = c(between["Clown",],between["Coco",],between["CT",],between["Denver",],between["Dio",],between["Jacob",],between["Josh",],between["Lisa",],between["Liz",],between["Mark",],between["Megan",],between["Megan O",],between["Mel",],between["Neb",],between["Zach",],between["Zanny",])
)
ggplot(betweenness_df, aes(x=eps,y=betweenness, group = cast)) + geom_line(aes(color = cast)) + ggtitle("Vertex Betweenness of Cast Per Episode") + xlab("Episodes") + ylab("Vertex Betweenness") + theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
```


