---
title: "Analysis"
author: "Eddie Kingston"
date: "2/8/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
ep1_day0_graph <- graph.adjacency(ep1_day0)
V(ep1_day0_graph)$indegree   <- igraph::degree(ep1_day0_graph, mode = "in")
V(ep1_day0_graph)$outdegree  <- igraph::degree(ep1_day0_graph, mode = "out")
V(ep1_day0_graph)$degree <- igraph::degree(ep1_day0_graph, mode = "total")
V(ep1_day0_graph)$closeness  <- igraph::closeness(ep1_day0_graph, mode = "total")
V(ep1_day0_graph)$betweeness <- igraph::betweenness(ep1_day0_graph, normalized = TRUE)
stats <- as_data_frame(ep1_day0_graph, what = "vertices")
stats_degree <- with(stats, {
 cbind(
   indegree   = quantile(indegree, c(.025, .5, .975), na.rm = TRUE),
   outdegree  = quantile(outdegree, c(.025, .5, .975), na.rm = TRUE),
   degree     = quantile(degree, c(.025, .5, .975), na.rm = TRUE),
   closeness  = quantile(closeness, c(.025, .5, .975), na.rm = TRUE),
   betweeness = quantile(betweeness, c(.025, .5, .975), na.rm = TRUE)
 )
})
stats_degree
```


```{r}
stats_merge <- function(g) {
  g <- graph.adjacency(g)
  cbind(
    degree = igraph::degree(g),
    vertex_density = igraph::degree(g)/(2*length(V(g))-2),
    vertex_betweenness = igraph::betweenness(g),
    reciprocity = reciprocity(g)
  )
}
```


```{r}
(ep1_day0_stats <- stats_merge(ep1_day0))
```
```{r}
(ep1_day1_stats <- stats_merge(ep1_day1))
```


```{r}
un <- function(g,m) {
  g <- graph_from_adjacency_matrix(g)
  m <- graph_from_adjacency_matrix(m)
  union <- union(g,m)
  un <- union(union,graph_from_adjacency_matrix(ep1_day1))
  u_mat <- as_adjacency_matrix(un)
  row_order <- sort(rownames(u_mat))
  col_order <- sort(colnames(u_mat))
  u_mat <- u_mat[row_order,col_order]
  un <- graph.adjacency(u_mat)
}
stats_tribes <- function(un) {
  cbind(
    degree = igraph::degree(un),
    vertex_density = igraph::degree(un)/(2*length(V(un))-2),
    vertex_betweenness = igraph::betweenness(un),
    reciprocity = reciprocity(un)
  )
}
(ep1_day1_tribes <- stats_tribes(un(ep1_day1_g1,ep1_day1_m1)))
```
```{r}
(ep1_day2_stats <- stats_tribes(un(ep1_day2_g1,ep1_day2_m1)))
```

```{r}
(ep1_day3_stats <- stats_tribes(un(ep1_day3_g1,ep1_day3_m1)))
```

```{r}
ep2_day4_stats <- stats_tribes(un(ep2_day4_g1,ep2_day4_m1))
(ep2_day4_stats <- ep2_day4_stats[-2,]) # Coco voted out
```

```{r}
ep2_day7_stats <- stats_tribes(un(ep2_day7_g1,ep2_day7_m1))
(ep2_day7_stats <- ep2_day7_stats[-2,])
```

```{r}
ep3_day9_stats <- stats_tribes(un(ep3_day9_g1,ep3_day9_m1))
(ep3_day9_stats <- ep3_day9_stats[-c(2,7),])
```

```{r}
ep3_day10_stats <- stats_tribes(un(ep3_day10_g1, ep3_day10_m1))
(ep3_day10_stats <- ep3_day10_stats[-c(2,7),])
```

```{r}
ep4_day10_stats <- stats_tribes(un(ep4_day10_g2,ep4_day10_m2))
(ep4_day10_stats <- ep4_day10_stats[-c(2,7,11),])
```

```{r}
ep5_day13_stats <- stats_tribes(un(ep5_day13_g2,ep5_day13_m2))
(ep5_day13_stats <- ep5_day13_stats[-c(2,6,7,11),])
```

```{r}
ep6_day14_stats <- stats_tribes(un(ep6_day14_g2,ep6_day14_m2))
(ep6_day14_stats <- ep6_day14_stats[-c(2,6,7,9,11),])
```

```{r}
(ep7_day16_stats <- stats_merge(ep7_day16))
```

```{r}
(ep8_day19_stats <- stats_merge(ep8_day19))
```

```{r}
(ep9_day21_stats <- stats_merge(ep9_day21))
```

```{r}
(ep9_day22_stats <- stats_merge(ep9_day22))
```

```{r}
(ep9_day23_stats <- stats_merge(ep9_day23))
```

```{r}
(ep9_day24_stats <- stats_merge(ep9_day24))
```

```{r}
(ep10_day26_stats <- stats_merge(ep10_day26))
```

```{r}
(finale_day27_stats <- stats_merge(finale_day27))
```
```{r}
(finale_day28_stats <- stats_merge(finale_day28))
```

```{r}
sort(ep1_day3_stats[,2])
```

```{r}
sort(ep2_day7_stats[,2])
```

```{r}
sort(ep3_day10_stats[,2])
```

```{r}
sort(ep4_day10_stats[,2])
```

```{r}
sort(ep5_day13_stats[,2])
```

```{r}
sort(ep6_day14_stats[,2])
```

```{r}
sort(ep7_day16_stats[,2])
```

```{r}
sort(ep8_day19_stats[,2])
```

```{r}
sort(ep9_day22_stats[,2]) # Ep 9_1
```
```{r}
sort(ep9_day23_stats[,2]) # Ep 9_2
```


```{r}
sort(ep9_day24_stats[,2]) # Ep 10
```

```{r}
sort(ep10_day26_stats[,2]) # Ep 11
```

```{r}
sort(finale_day27_stats[,2])
```


```{r}
order <- c("Megan O", "CT", "Neb", "Mark", "Lisa", "Clown", "Mel", "Zach", "Dio", "Denver", "Zanny", "Liz", "Jacob", "Megan", "Josh", "Coco")
eps <- c("Ep 1", "Ep 2", "Ep 3", "Ep 4", "Ep 5", "Ep 6","Ep 7", "Ep 8", "Ep 9_1", "Ep 9_2", "Ep10", "Ep11_1", "Ep11_2", "f1", "f2", "f3")
vert_dens_ranks <- matrix(0,16,16,dimnames=list(order, eps))
vert_dens_ranks[1,] <- c(10,6,7,11,7,6,1,2,4,1,1,1,1,rep(NA,3)) # Megan O
vert_dens_ranks[2,] <- c(4,5,3,3,2,3,6,4,1,1,1,1,1,rep(NA,3)) # CT 
vert_dens_ranks[3,] <- c(7,6,7,10,8,6,5,4,2,1,3,1,1,rep(NA,3))  # Neb
vert_dens_ranks[4,] <- c(12,12,13,13,12,10,10,8,8,4,4,4,4,rep(NA,3)) # Mark
vert_dens_ranks[5,] <- c(1,1,1,1,1,1,1,1,5,4,5,4,rep(NA,4)) # Lisa
vert_dens_ranks[6,] <- c(7,8,4,5,5,5,9,8,7,7,3,rep(NA,5)) # Clown
vert_dens_ranks[7,] <- c(11,10,11,7,8,9,6,6,5,4,rep(NA,6)) # Mel
vert_dens_ranks[8,] <- c(2,2,2,1,2,2,1,2,3,rep(NA,7))  # Zach
vert_dens_ranks[9,] <- c(7,10,9,4,4,3,6,6,rep(NA,8))  # Dio
vert_dens_ranks[10,] <- c(4,3,4,7,8,6,1,rep(NA,9)) # Denver
vert_dens_ranks[11,] <- c(14,12,13,12,8,11,rep(NA,10)) # Zanny
vert_dens_ranks[12,] <- c(6,8,9,5,5,rep(NA,11)) # Liz
vert_dens_ranks[13,] <- c(2,3,4,7,rep(NA,12)) # Jacob
vert_dens_ranks[14,] <- c(13,14,12,rep(NA,13))  # Megan
vert_dens_ranks[15,] <- c(15,15,rep(NA,14)) # Josh
vert_dens_ranks[16,] <- c(15,rep(NA,15)) # Coco
vert_dens_df <- data.frame(
  cast = sort(rep(cast,16)),
  eps = rep(eps,16)
)
vert_dens_df <- vert_dens_df %>% mutate(
  ranks = c(vert_dens_ranks["Clown",],vert_dens_ranks["Coco",],vert_dens_ranks["CT",],vert_dens_ranks["Denver",],vert_dens_ranks["Dio",],vert_dens_ranks["Jacob",],vert_dens_ranks["Josh",],vert_dens_ranks["Lisa",],vert_dens_ranks["Liz",],vert_dens_ranks["Mark",],vert_dens_ranks["Megan",],vert_dens_ranks["Megan O",],vert_dens_ranks["Mel",],vert_dens_ranks["Neb",],vert_dens_ranks["Zach",],vert_dens_ranks["Zanny",])
)
```

```{r}
ggplot(vert_dens_df, aes(x=eps,y=ranks, group = cast)) + geom_line(aes(color = cast)) + scale_y_reverse() + ggtitle("Average Vertex Densities of Cast Per Episode") + xlab("Episodes") + ylab("Ranks") + theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
```


```{r}
sort(ep1_day3_stats[,3])
```

```{r}
sort(ep2_day7_stats[,3])
```

```{r}
sort(ep3_day10_stats[,3])
```

```{r}
sort(ep4_day10_stats[,3])
```

```{r}
sort(ep5_day13_stats[,3])
```

```{r}
sort(ep6_day14_stats[,3])
```

```{r}
sort(ep7_day16_stats[,3])
```

```{r}
sort(ep8_day19_stats[,3])
```

```{r}
sort(ep9_day22_stats[,3])
```


```{r}
sort(ep9_day23_stats[,3])
```

```{r}
sort(ep9_day24_stats[,3])
```

```{r}
sort(ep10_day26_stats[,3])
```

```{r}
sort(finale_day27_stats[,3])
```

```{r}
sort(finale_day28_stats[,3])
```

```{r}
ggplot(vert_dens_df, aes(x=eps,y=densities, group = cast)) + geom_line(aes(color = cast)) + ggtitle("Vertex Densities of Cast Per Episode") + xlab("Episodes") + ylab("Densities")
```

```{r}
ggplot(betweenness_df, aes(x=eps,y=betweenness, group = cast)) + geom_line(aes(color = cast)) + ggtitle("Vertex Betweenness of Cast Per Episode") + xlab("Episodes") + ylab("Vertex Betweenness")
```

```{r}
clust_opt_tribes <- function(g,m) {
  g <- graph_from_adjacency_matrix(g)
  m <- graph_from_adjacency_matrix(m)
  old_union <- union(g,m)
  new_union <- union(old_union,graph_from_adjacency_matrix(ep1_day1))
  clust <- cluster_optimal(old_union)
  plot(clust,old_union)
  print(clust)
}
clust_opt_tribes(ep1_day3_g1,ep1_day3_m1)
```
Interesting thing to note here: does almost a perfect job at capturing tribes, except for having Coco being a part of Makassan instead of Gurundji
```{r}
clust_opt_tribes(ep6_day14_g2,ep6_day14_m2)
```


```{r}
clust_opt_merge <- function(g) {
  g <- graph_from_adjacency_matrix(g)
  un <- union(g,graph_from_adjacency_matrix(ep1_day1))
  clust <- cluster_optimal(g)
  plot(clust,g)
  print(clust)
}
clust_opt_merge(ep7_day16)
```
Captures the people who were in Makassan 1.0 and Gurundji 2.0, and ropes Clown in with them.
Another interesting thing to note: very small modularity here.

```{r}
clust_opt_merge(ep8_day19)
```

```{r, include = FALSE}
clust_mods <- c(modularity(clust_opt_tribes(ep1_day3_g1,ep1_day3_m1)),modularity(clust_opt_tribes(ep2_day7_g1,ep2_day7_m1)),modularity(clust_opt_tribes(ep3_day10_g1,ep3_day10_m1)),modularity(clust_opt_tribes(ep4_day10_g2,ep4_day10_m2)),modularity(clust_opt_tribes(ep5_day13_g2,ep5_day13_m2)),modularity(clust_opt_tribes(ep6_day14_g2,ep6_day14_m2)),modularity(clust_opt_merge(ep7_day16)),modularity(clust_opt_merge(ep8_day19)), modularity(clust_opt_merge(ep9_day23)),modularity(clust_opt_merge(ep9_day24)),modularity(clust_opt_merge(ep10_day26)),modularity(clust_opt_merge(finale_day27)),modularity(clust_opt_merge(finale_day28)))
# Add in the rest of the graphs - trying to see if any of these results have more than 3 groups
```

```{r}
which.max(clust_mods) # Episode 2
clust_opt_tribes(ep2_day7_g1,ep2_day7_m1)
```
This clustering splits the tribes perfectly. The only reason the modularity is so high is because the people within each cluster were only allowed to talk with each other, so this doesn't give us much of anything insightful.

```{r}
which.min(clust_opts)
```
```{r}
clust_opt_merge(ep9_day24) # Episode 10
```
For all intents and purposes, this modularity is basically 0. This means the edge distributions might as well have been random.

```{r}
mod_df <- data.frame(
  eps = eps,
  mods = c(clust_mods,rep(NA,3))
)
ggplot(mod_df,aes(x=eps,y=mods)) + geom_point(fill="blue") + geom_path(color="blue") + ggtitle("Modularities of networks across episodes") + xlab("Episodes") + ylab("Modularities") + theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
```
Modularities take a big hit right around the merge, almost certainly due to the lack of tribe structures.


```{r}
clust_opt_merge(ep1_day0)
clust_opt_tribes(ep1_day1_g1,ep1_day1_m1)
clust_opt_tribes(ep2_day7_g1,ep2_day7_m1)
clust_opt_tribes(ep3_day10_g1,ep3_day10_m1)
clust_opt_tribes(ep4_day10_g2,ep4_day10_m2)
clust_opt_tribes(ep5_day13_g2,ep5_day13_m2)
clust_opt_tribes(ep6_day14_g2,ep6_day14_m2)
clust_opt_merge(ep7_day16)
clust_opt_merge(ep8_day19)
clust_opt_merge(ep9_day22)
clust_opt_merge(ep9_day23)
clust_opt_merge(ep9_day24)
clust_opt_merge(ep10_day26)
clust_opt_merge(finale_day27)
clust_opt_merge(finale_day28)
```


```{r}
clust_edge_tribes <- function(g,m) {
  g <- graph_from_adjacency_matrix(g)
  m <- graph_from_adjacency_matrix(m)
  old_union <- union(g,m)
  clust <- cluster_edge_betweenness(old_union)
  plot(clust,old_union)
}
clust_edge_merge <- function(g) {
  g <- graph_from_adjacency_matrix(g)
  un <- union(g,graph_from_adjacency_matrix(ep1_day1))
  clust <- cluster_edge_betweenness(g)
  plot(clust,g)
}
```


```{r}
clust_edge_merge(ep1_day0)
clust_edge_tribes(ep1_day1_g1,ep1_day1_m1)
clust_edge_tribes(ep2_day7_g1,ep2_day7_m1)
clust_edge_tribes(ep3_day10_g1,ep3_day10_m1)
clust_edge_tribes(ep4_day10_g2,ep4_day10_m2)
clust_edge_tribes(ep5_day13_g2,ep5_day13_m2)
clust_edge_tribes(ep6_day14_g2,ep6_day14_m2)
clust_edge_merge(ep7_day16)
clust_edge_merge(ep8_day19)
clust_edge_merge(ep9_day22)
clust_edge_merge(ep9_day23)
clust_edge_merge(ep9_day24)
clust_edge_merge(ep10_day26)
clust_edge_merge(finale_day27)
clust_edge_merge(finale_day28)
```

```{r}
clust_eig_tribes <- function(g,m) {
  g <- graph_from_adjacency_matrix(g)
  m <- graph_from_adjacency_matrix(m)
  old_union <- union(g,m)
  clust <- cluster_leading_eigen(old_union)
  plot(clust,old_union)
}
clust_eig_merge <- function(g) {
  g <- graph_from_adjacency_matrix(g)
  un <- union(g,graph_from_adjacency_matrix(ep1_day1))
  clust <- cluster_leading_eigen(g)
  plot(clust,g)
}
```

```{r}
clust_eig_merge(ep1_day0)
clust_eig_tribes(ep1_day1_g1,ep1_day1_m1)
clust_eig_tribes(ep2_day7_g1,ep2_day7_m1)
clust_eig_tribes(ep3_day10_g1,ep3_day10_m1)
clust_eig_tribes(ep4_day10_g2,ep4_day10_m2)
clust_eig_tribes(ep5_day13_g2,ep5_day13_m2)
clust_eig_tribes(ep6_day14_g2,ep6_day14_m2)
clust_eig_merge(ep7_day16)
clust_eig_merge(ep8_day19)
clust_eig_merge(ep9_day22)
clust_eig_merge(ep9_day23)
clust_eig_merge(ep9_day24)
clust_eig_merge(ep10_day26)
clust_eig_merge(finale_day27)
clust_eig_merge(finale_day28)
```


